\documentclass[12pt]{amsart}
\usepackage{amssymb,amsmath,amsthm,graphicx,verbatim,amsbsy}

\usepackage[margin=1in]{geometry}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{noname}[theorem]{}
\newtheorem{sublemma}{}[theorem]
\newtheorem{conjecture}[theorem]{Conjecture}

\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}

\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

\numberwithin{equation}{section}

\begin{document}

\begin{flushright}
Name:\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_
\end{flushright}
\vspace{10pt}
\begin{center}
Introduction to Cryptography

Multiplicative Cipher
\end{center}


\begin{enumerate}
\item Write a program in Python that 
\begin{enumerate}
\item prompts the user for a lowercase message;
\item prompts the user for a multiplicative key;
\item performs the multiplicative encryption to each letter modulo $26$;
\item prints the encrypted message.
\end{enumerate}
\item Suppose your message is the string ``abcdefghijklmnopqrstuvwxyz". Write a program which uses a for-loop to perform the multiplicative cipher to this message for each key from $0$ to $25$. Which of these keys makes the encrypted alphabet a valid substitution cipher? Make a conjecture about the relationship between the valid keys and the number $26$.
\item Rather than encrypting each letter individually, we can instead encrypt blocks of letters simultaneously to provide more security. As an example, the plaintext message ``fatcat" can be decomposed into two-letter blocks as ``fa" ``tc" ``at". Using our usual scheme, the block ``fa" is associated with the number 500, the block ``tc" is associated with the number 1902, and the block ``at" is associated with the number 19. What are we doing to accomplish this transformation? Encrypt each of these blocks by multiplying by $11\mod 2800$. What do you notice if you instead multiplied by $1400\mod 2800$? 
\item Suppose $A$ and $n$ are integers so that $Ax\equiv 0\mod n$ for some integer $x\not\equiv 0\mod n$. Make a conjecture about the relationship between $A$ and $n$. If $A$ is interpreted as a multiplicative key, conjecture when $A$ will be a valid key.
\item Compute the greatest common divisor of $234$ and $500$.
\item Compute the greatest common divisor of $1331$ and $2431$.
\end{enumerate}
\vfill


\end{document}