\documentclass[12pt]{amsart}
\usepackage{amssymb,amsmath,amsthm,graphicx,verbatim,amsbsy}

\usepackage[margin=1in]{geometry}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{noname}[theorem]{}
\newtheorem{sublemma}{}[theorem]
\newtheorem{conjecture}[theorem]{Conjecture}

\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}

\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

\numberwithin{equation}{section}

\begin{document}

\begin{flushright}
Name:\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_
\end{flushright}
\vspace{10pt}
\begin{center}
Introduction to Cryptography

Diophantine Equations
\end{center}


\begin{enumerate}
\item Determine whether the following Diophantine equations have solutions. You do not need to solve the equations.
\begin{enumerate}
\item $10X+15Y=1$
\item $9X+16Y=1$
\item $24X+56Y=1$
\end{enumerate}
\item Find integers $X$ and $Y$ that solve the following Diophantine equations, or show that they do not have a solution.
\begin{enumerate}
\item $223X+75Y=1$
\item $35X+49Y=1$
\item $7X+24Y=1$
\end{enumerate}
\item Find an integer $X$ that satisfy the following equations, or show that no such number exists. 
\begin{enumerate}
\item $75X\equiv 1\mod 223$
\item $35X\equiv 1 \mod 49$
\item $7X\equiv 1 \mod 24$
\end{enumerate}
\item
\begin{enumerate}
\item Find a solution to the Diophantine equation $13X+8Y=1$.
\item Find a solution to the Diophantine equation $21X+13Y=1$.
\item Based on your answers, make a conjecture for a solution to the following Diophantine equation $F_{n+1}X+F_{n}Y=1$.
\end{enumerate}
\item If $(\widetilde{X},\widetilde{Y})$ is a solution to the Diophantine equation $AX+BY=1$, what is a solution to the Diophantine equation $AX+BY=2$? What about $AX+BY=n$ where $n$ is an integer?
\item You have a $7$-liter bucket and a $24$-liter bucket. Using these, you can add or remove exactly $7$ or $24$ liters of water at a time into or out of a large tank. If the large tank begins empty, explain how you can use the buckets to end with exactly $2$ liters of water in the large tank.
\item What if you instead have a $4$-liter bucket and a $6$-liter bucket. Can you use the buckets to end with exactly $1$ liter of water in the large tank? What about $2$ liters?
\item If $(\widetilde{X},\widetilde{Y})$ is a solution to the Diophantine equation $AX+BY=1$, and if $t$ is any integer, show that $(\widetilde{X}+Bt,\widetilde{Y}-At)$ is also a solution to this Diophantine equation.
\item Use the result from the previous problem to find infinitely many solutions to the following Diophantine equations, if a solution exists.
\begin{enumerate}
\item $223X+75Y=1$
\item $35X+49Y=1$
\item $7X+24Y=1$
\end{enumerate}
\item (Optional Challenge Problem): When Dr. Benge cashed a check at his bank, the teller mistook the number of cents for the number of dollars and vice versa. Unaware of this, Dr. Benge spent $68$ cents and then noticed to his surprise that he had twice the amount of the original check. Determine the smallest value for which the check could have been written.
\end{enumerate}
\vfill


\end{document}