\documentclass[12pt]{amsart}
\usepackage{amssymb,amsmath,amsthm,graphicx,verbatim,amsbsy}

\usepackage[margin=1in]{geometry}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{noname}[theorem]{}
\newtheorem{sublemma}{}[theorem]
\newtheorem{conjecture}[theorem]{Conjecture}

\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}

\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

\numberwithin{equation}{section}

\begin{document}

\begin{flushright}
Name:\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_
\end{flushright}
\vspace{10pt}
\begin{center}
Introduction to Cryptography

Prime and Composite Numbers
\end{center}

\begin{enumerate}

\item Determine whether the following numbers are prime or composite. Record the number of seconds needed to determine each result.
\begin{enumerate}
\item $116666666666611$
\item $1000000000100011$
\item $13000000000000019$
\item $12345689798654321$
\end{enumerate}

\item Consider an ideal computer with a $4$ gigahertz processor which can perform $4$ billion arithmetic operations per second. Approximately how many seconds would it take such a computer running your program to verify that a $20$ digit number is prime? What about a $200$ digit number? How many seconds old is the universe?

\item Let $\pi(n)$ be the number of prime numbers less than an integer $n$. For example, $\pi(10)=4$, and $\pi(20)=8$. Write a program in Python to compute $\pi(100000)$. 

Note: The {\bf Sieve of Eratosthenes} from class will be useful.

\item The Prime Number Theorem states that $$\lim_{n\rightarrow\infty}\frac{\pi(n)}{\frac{n}{\ln(n)}}=1,$$ which means that $\pi(n)$ is approximately equal to $\frac{n}{\ln(n)}$ whenever $n$ is large. Demonstrate the Prime Number Theorem using a few large numbers $n$.

\item Using the Prime Number Theorem, approximate the number of $10$ digit prime numbers. Approximate the probability that a US phone number is a prime number.

\item The twin prime conjecture states that there are infinitely many prime numbers $p$ such that $p+2$ or $p-2$ is also prime. As examples, $3$ and $5$ are twin primes, so are $17$ and $19$. Write a program in Python that creates a list of the first $1000$ twin primes.
\end{enumerate}
\end{document}