\documentclass[12pt]{amsart}
\usepackage{amssymb,amsmath,amsthm,graphicx,verbatim,amsbsy}

\usepackage[margin=1in]{geometry}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{noname}[theorem]{}
\newtheorem{sublemma}{}[theorem]
\newtheorem{conjecture}[theorem]{Conjecture}

\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}

\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

\numberwithin{equation}{section}

\begin{document}

\begin{flushright}
Name:\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_
\end{flushright}
\vspace{10pt}
\begin{center}
Introduction to Cryptography

Homework 1
\end{center}

Answer the following questions.

\begin{enumerate}
\item Determine which of the following statements are true and which are false.
\begin{enumerate}
\item $144\equiv34\mod 10$
\item $99\equiv -1 \mod 8$
\item $144\equiv 12\mod 7$
\item $20\equiv -20\mod 40$
\end{enumerate}
%\vspace{10pt}
%\item 
%\begin{enumerate}
%\item Find the remainder whenever $137$ is %divided by $13$.
%\item Find the remainder whenever $96$ is %divided by $13$.
%\item Given that $13152=137\times96$, find the %remainder whenever $13152$ is divided by $13$. 
%\end{enumerate}
\vspace{10pt}
\item Write out several integers $x$ satisfying $x\equiv 1\mod 2$. What type of integers satisfy this equation?
\vspace{10pt}
\item Determine whether the following statements are true or false. If a statement is true, explain why. If it is false, give a counterexample.
\begin{enumerate}
\item All numbers that are divisible by $5$ are also divisible by $10$.
\item All number that are divisible by $10$ are also divisible by $5$.
\item The remainder whenever an integer $x$ is divided by $5$ is the same as the remainder whenever $x$ is divided by $10$.
\end{enumerate}
%\vspace{10pt}
%\item Show that $\left( x+y\right)^3\equiv x^3+y^3 \mod 3$.
\vspace{10pt}
\item Encrypt the following message by shifting each letter in the alphabet by $13$ to the right. Message: I LOVE MATH.
\vspace{10pt}
\item Suppose the following encrypted message was obtained by shifting each letter of the original message by $5$ to the right. What is the original message? Encrypted message: DTZ SJAJW PSTB BMJS DTZ SJJI XJHWJHD.
\end{enumerate}
\vfill


\end{document}